\newcommand{\HRule}{\rule{\linewidth}{0.2mm}} % Defines a new command for the horizontal lines, change thickness here

\begin{titlepage}
\noindent {\Huge NISEI Comprehensive Rules Document}\\[10pt]
This rules document is to be used as reference material. It is not intended to be read straight through. If you still have questions after consulting this document, please ask us online via \href{mailto:rules@nisei.net}{email} or \href{https://twitter.com/NISEI_Rules}{Twitter}.\\[10pt]
This is \textbf{version 1.4} of this document, effective \textbf{20 December 2019}.\\\\
\noindent {\Large Summary of Changes}\\[10pt]
Changes from version 1.2 are \textcolor{Bittersweet}{highlighted in orange}.
\begin{itemize}
	\item Added our email address.
	\item Performed a complete rewrite and reorganization of section 1.14 (Targets) and section 9 (Abilities).
	\item Updated imprecise terminology throughout the document to improve clarity now that terms like ``using'' and ``instruction'' are used extensively in the rules for abilities.
	\item Added rules for interrupts (section 9.8) and the interrupt symbol (rule 1.3.10).
	\item Added rules for double-sided identities (rule 1.5.4d, rule 1.6b, and rule 3.1.1a).
	\item Clarified that the terms ``spend'' and ``pay'' are synonyms (Rule 1.10.3c).
	\item Expanded the definition of the ``source'' of an ability and moved these rules from section 1.13.5 to section 9.1.3.
	\item Codified rules about inherent costs (rule 1.15.4a and rule 1.15.4b).
	\item Added “if you do'' expressions to the list of ways nested costs can be formatted (section 1.15.10).
	\item Clarified that if a replacement effect replaces adding a card to a hand, score area, or discard pile, that card can still count as drawn, scored, stolen, or trashed (rule 1.8.5, rule 1.16.3f, and rule 1.18.1a).
	\item Defined ``advanced card'' (rule 1.17.3).
	\item Expanded rules on ``reveal'' and card visibility in general. Moved these rules from section 8.1 to their own section (section 1.20).
	\item Added ``starting memory limit'' to parts of a card (section 2.10).
	\item Added new subtypes (section 2.16.7).
	\item Defined reminder text (rule 2.17.3).
	\item Added rules for lockdown operations (rule 3.5.1c).
	\item Clarified rules for the implicit duration of strength-boosting icebreaker abilities (section 3.9.5).
	\item Removed the concept of ``return to base strength'' and issued errata to System Seizure and Gebrselassie to clarify how their abilities work. 
	\item Defined ``location'' and ``destination'' (section 4.1.7).
	\item Clarified the meaning of a search ``for cards with different names'' (rule 4.2.2e).
	\item Added rules for ``Limit 1 remote server.'' (rule 4.7.8h) and ``Remote server only.'' (rule 8.2.12).
	\item Added rules for the set-aside zone (section 4.8).
	\item Clarified the rules for “if successful” abilities (section 6.7.3).
	\item Simplified the steps of installing and playing cards (section 8.3 and section 8.6).
	\item Updated the rule for facedown Runner cards being trashed so that they are not turned face up until after entering the heap (rule 8.4.4).
	\item Added rules for dividing an ability into instructions (section 9.10).
	\item Updated rules about the results of a trace attempt (rule 10.8.5) to match the new ability classification.
	\item Removed the ``Quantifiers'' section (formerly section 10.9). The rules for ``additional'' have been deprecated, and The Cleaners, Defective Brainchips, Daily Business Show, and Laguna Velasco District have been given appropriate errata. The rules for ``all'' and ``for each'' have been moved to section 9.11.2.
	\item Added rules defining ``load'' and ``empty'' (section 10.9).
	\item Updated which version of a card is definitive to better handle wording updates performed when a card is reprinted (rule 11.1.2).
	\item Issued errata to update wording and add the interrupt symbol to the abilities on Net Shield, Zaibatsu	Loyalty, Muresh Bodysuit, Tyr's Hand, The Cleaners, Tori Hanzō, Progenitor, Quianju PT, Defective Brainchips, Harbinger, Jesminder Sareen, Laguna Velasco District, Marilyn Campaign, Patchwork, Flip	Switch, and The Class Act.
	\item Issued errata to Sneakdoor Beta, Rielle ``Kit'' Peddler, and Omar Keung to clarify the timing of their effects.
	\item Issued errata to Mr. Li, Bug, Daily Business Show, Political Dealings, Raman Rai, Find the Truth,	Corporate Defector, and Jinja City Grid so that their abilities manipulate cards before those cards are	drawn, and therefore the affected cards are not mixed with other cards in the player's hand. In most cases this involved making the ability an interrupt. In one case it involved a sacrifice to Apex.
	\item Issued non-functional errata to update the wording of Early Bird, Universal Connectivity Fee, Jinteki	Biotech: Life Imagined, Back Channels, Rigged Results, Injection Attack, Cold Read, Severnius Stim Implant.
	\item Corrected formatting of reminder text (italics) in the errata for Demolition Run and Freedom Khumalo.
	\item Removed errata from Power Shutdown.
	\item Issued non-functional errata to Stimhack to host credits on itself instead of adding them to the Runner's credit pool.
	\item Issued non-functional errata to clarify Wyrm's ice strength-lowering effect.
	\item Issued functional errata to Disrupter so that its interrupt sets the base trace strength of a trace attempt to 0 instead of preventing and recreating the entire trace attempt.
	\item Issued errata to Architect to clarify that the game engine can trash it if its location becomes illegal (such as by a ``Limit 1 remote server'' ability becoming active).
	\item Issued non-functional errata to Forger to split its ``avoid'' and ``remove'' modes into separate abilities and clarify that they have different timing.
	\item Issued errata to Rip Deal to allow it to interact more clearly with multi-access abilities.
	\item Issued non-functional errata to Skorpios Defense Systems to allow the Corp to be able to see which cards are being trashed before removing one from the game.
	\item Issued errata to correct the wording of Engram Flush.	
\end{itemize}

\end{titlepage}