\newcommand{\HRule}{\rule{\linewidth}{0.2mm}} % Defines a new command for the horizontal lines, change thickness here

\begin{titlepage}
\noindent {\Huge NISEI Comprehensive Rules Document}\\[10pt]
This rules document is to be used as reference material. It is not intended to be read straight through. If you still have questions after consulting this document, please contact us via \href{mailto:rules@nisei.net}{email} or \href{https://twitter.com/NISEI_Rules}{Twitter}.\\[10pt]
This is \textbf{version 1.3} of this document, effective \textbf{2 August 2019}.\\\\
\noindent {\Large Summary of Changes}\\[10pt]
Changes from version 1.2 are \textcolor{Bittersweet}{highlighted in orange}.
\begin{itemize}
	\item Slightly reworked the definitions of actions and action phases. A player can no longer take an action outside their action phase under any circumstances. In particular, if an effect would try to allow a player	to take an action after a Terminal operation has resolved, nothing happens (\hyperlink{page.i}{rule~5.2.5} and \hyperlink{page.i}{section~5.4}).
	\item Clarified how to distinguish actions for the purposes of determining whether they are ``the same'' or ``different'', as referenced by \card{Jeeves Model Bioroids} and \card{MirrorMorph: Endless Iteration} (\hyperlink{page.i}{section~5.2.6}).
	\item Clarified and expanded the Run Ends Phase and the procedure for resolving an ``end the run'' effect. In	particular, version 1.2 of the Comprehensive Rules did not adequately specify what to do if an effect
	ends the run while a paid ability window or one or more reaction windows are open. The rules for the Run Ends Phase now explicitly state which priority windows are completed normally after an ``end the run'' instruction resolves, and which priority windows are closed without resolving any of their remaining pending abilities (\hyperlink{page.i}{section~6.1}, \hyperlink{page.i}{section~6.8.2}, and \hyperlink{page.i}{step~6.9.6a}). \hyperlink{page.i}{Rule 6.5.5a} and \hyperlink{page.i}{section~12.3} have also been updated to refer to these expanded rules as appropriate.
	\item Updated and clarified rules about successful and unsuccessful runs. ``Successful'' is now explicitly stated to be a label applied to a run, so that declaring a run to be successful is separate from the procedure for accessing cards. Added a definition for the corresponding ``unsuccessful run'' label, and	expanded rules about when that label should or should not be applied. Issued errata to Crisium Grid	making use of these changes to simplify the card with little effect on its practical functionality (\hyperlink{page.i}{rule 6.7.2}, \hyperlink{page.i}{section~6.8.4}, \hyperlink{page.i}{step~6.9.5e}, \hyperlink{page.i}{step~6.9.6c}, and \hyperlink{page.i}{section~11.2.17}).
	\item Corrected an error in \hyperlink{page.i}{rule 4.7.8f}, where the rule about ending the run due to a server ceasing to exist had been written too generally.
\end{itemize}

\end{titlepage}